---
title: 'Dynamic Plot: Normally distributed random numbers'
author: "Mukesh Kanchan"
date: "Wednesday, October 15, 2014"
output: html_document
---

This application plots normally distributed random data generated by following R fucntion:
```{r eval=FALSE}
rnorm(number, mean, standard_deviation)
```
User Guide:
----------

To use this application, one can manupulate following input parameters:

1. Number of ramdom samples: 
   
   
        >Select number of data points for plot, ranging from 100 to 500.  
2. Plot type:     
   
   
        >Check Point for plot with points (circle)
        >Check Line for line plot
        >Check both to show both point and line
        >No plotting, if none checked
3. Set mean:
   
   
        >Use slider to set mean to use for rnorm function 
        >Ranging from -5 to 5
4. Set standard deviation:
   
   
        >Use slider to set standard deviation for rnorm function, 
        >Ranging from 0 to 1
5. Random Data Seed/Change Seed:
   
   
        >Type in a integer value to change the seed for random number geberation
        >You MUST click "Change Seed" button after entering a new value
6. Plot color:
   
   
        >Select a color (Black, Blue, Red , Green) for plot

    
---------------------------------------------------------------------------
    
Change in input widgets are reflected on output in real time, except for "Random Data Seed". By design, application needs user to click "Change Seed" button to have its effect on output. Following are the outputs:
    
    
1. Plot
   
   
        >A plot is generated with default selected value
        >It is updated when any value is changed OR "change seed" button is clicked 
        >Seed value is displayed in the main title of the chart
2. Summary
   
   
        >Summary of randomly generated data is displayed at the bottom.
        >R Function used for the this:
```{r eval=FALSE} 
        summary(data) 
``` 
        
